Recursive algorithms, branching coefficients and applications

### 2010-07-06 AffineLieAlgebras/InformalNotes/article.tex
Equation numbering simplified

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation}
  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
\end{equation}

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

@@

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
and take into account that the projection commutes with the multiplication:
\begin{eqnarray*}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{eqnarray*}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplify the first factor,
\begin{eqnarray*}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{eqnarray*}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
\begin{eqnarray*}
  \label{eq:13}
 \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
 \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
\end{eqnarray*}
The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we can rewrite the shifted weights
\begin{equation}
  \label{eq:30}
  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
\end{equation}

\begin{eqnarray*}
  \label{eq:14}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{eqnarray*}
The projector $\pi_{\mathfrak{a}}$ sends the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ to the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
  \begin{eqnarray*}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{eqnarray*}
Thus we obtain the relation
\begin{eqnarray*}
  \label{eq:9}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
\end{eqnarray*}
Let us rewrite the factor in the right-hand side:
\begin{equation}
  \label{eq:11}
    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
     -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
\end{equation}

For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
}\subset \frak{g}}\subset P_{\frak{a}}$:
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
\gamma \right) \neq 0\right\} .  \label{phi-d}
\end{equation}
From the relation \ref{eq:9} the obtained equation for the formal elements,
\begin{eqnarray*}
  \label{eq:16}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
  k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
\end{eqnarray*}
we can deduce the following property of the anomalous branching coefficients,
\begin{eqnarray*}
  \label{eq:17}
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
\end{eqnarray*}

>>>>

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
\end{equation*}

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation*}
%  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation*}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

@@

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
  \end{array}
\end{equation*}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
\begin{equation*}
%  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation*}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can consider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation*}
%  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation*}
and take into account that the projection commutes with the multiplication:
\begin{eqnarray*}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{eqnarray*}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation*}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation*}
and simplify the first factor,
\begin{eqnarray*}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{eqnarray*}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}\subset W$.
Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
\begin{equation}
  \label{eq:13}
  \begin{array}{c}
\fl \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
= \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
  \end{array}
\end{equation}
The fraction in the right-hand side of the equation looks like the character of some  $\mathfrak{a}_{\bot}$-module.
Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we can rewrite the shifted weights
\begin{equation*}
  \label{eq:30}
  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
\end{equation*}

\begin{eqnarray*}
  \label{eq:14}
\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{eqnarray*}
The projector $\pi_{\mathfrak{a}}$ sends the character ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ to the unit element of $\cal{E}$ multiplied by ${\rm dim}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$  :
  \begin{eqnarray*}
    \label{eq:15}
\fl    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{eqnarray*}
Thus we obtain the relation
\begin{equation}
  \label{eq:9}
  \begin{array}{c}
\fl  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
  \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
  \end{array}
\end{equation}
Let us rewrite the factor in the right-hand side:
\begin{equation}
  \label{eq:11}
    \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})} \left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}=
     -\sum_{\gamma\in P_{\mathfrak{a}}} s(\gamma)e^{-\gamma}
\end{equation}

For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
}\subset \frak{g}}\subset P_{\frak{a}}$:
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
\gamma \right) \neq 0\right\} .  \label{phi-d}
\end{equation}
From the relation \ref{eq:9} the obtained equation for the formal elements,
\begin{eqnarray*}
  \label{eq:16}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
  k_{\lambda }^{\left( \mu \right) }e^{\lambda } =\\
  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
\end{eqnarray*}
we can deduce the following property of the anomalous branching coefficients,
\begin{eqnarray}
  \label{eq:17}
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
\end{eqnarray}

To get the recurrent relations for the coefficients $k^{(\mu)}_{\xi+\gamma}$ we use the following procedure  (similar to that in \cite{ilyin812pbc}).
Let $\gamma_{0} $ be the lowest vector with respect to the natural ordering in $%
\co{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$ and decompose the defining relation (\ref{eq:11}),
\begin{equation*}
  \label{eq:18}
  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta^{+}_{\bot})}\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },
\end{equation*}
the equality (\ref{eq:17}) leads to the desired recurrent  relation for the anomalous branching coefficients:
\begin{eqnarray*}
  k_{\xi }^{\left( \mu \right) }=
  -\frac{1}{s\left( \gamma _{0}\right) }
  \left(
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}
    \left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
    \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
    \right.\\
    \left. +
    \sum_{\gamma \in \Gamma _{\frak{a}\subset \frak{g}}} s\left( \gamma +\gamma _{0}\right) k_{\xi+\gamma }^{\left( \mu \right) }
  \right)
\label{recurrent-relation}
\end{eqnarray*}
where the set
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
\label{fan-defined}
\end{equation}
 was introduced that is called the injection fan.
